EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-17 draft.tex
Rounding out and eliminating comments

However, when we compare the two
options, we find some subtle differences: When using one or two
workers, using 5 populations takes less time in most cases. 
In Table~\ref{tab:time} results with p-value of the two-tailed Wilcoxon
signed-ranks test was grater than the level of significance of 0.05 
(i.e., accepting the null hypothesis of inequality) are marked in boldface.
A reason for this could be that when having more populations, the migration
of individuals takes more time to reach to all of them.
% how come? - JJ  - Explained a bit more - M
For instance, when a single worker has 10 populations, only
after processing every one of them, it will start receiving mixed populations.  Although, in
all cases, and even with a single worker, populations are heterogeneous, but
mixed individuals take more time to propagate. % which advantage? - JJ - Individuals from other pops - M
With four workers, almost the same
results can be achieved regardless of our selection between five or ten
populations. Also, there is not much difference between 4 and 8 workers, when
using five populations, which might indicate that some workers are
idling while populations are being processed by other workers. In
general, we can observe that keeping a ratio between the number of workers and populations a bit over 1:1  exploits better the computing
resources available. This also decreases the relation between the
overhead needed to migrate and process incoming and outgoing
population and the total computing time: more populations will need
more time to do that.

>>>>

However, when we compare the two
options, we find some subtle differences: When using one or two
workers, using 5 populations takes less time in most cases. 
In Table~\ref{tab:time} results with p-value of the two-tailed Wilcoxon
signed-ranks test was grater than the level of significance of 0.05 
(i.e., accepting the null hypothesis of inequality) are marked in boldface.
A reason for this could be that when having more populations, the migration
of individuals takes more time from the beginning to reach to all of them.
For instance, when a single worker has 10 populations, only
after processing every one of them, it will start receiving mixed populations.  Although, in
all cases, and even with a single worker, populations are heterogeneous, 
 individuals resulting from the mixing of populations take more time to propagate. 
With four workers, almost the same
results can be achieved regardless of our selection between five or ten
populations. Also, there is not much difference between 4 and 8 workers, when
using five populations, which might indicate that some workers are
idling while populations are being processed by other workers. In
general, we can observe that keeping a ratio between the number of workers and populations a bit over 1:1  exploits better the computing
resources available. This also decreases the relation between the
overhead needed to migrate and process incoming and outgoing
population and the total computing time: more populations will need
more time to do that.
